---
title: "Analysis of questions: pilot e01"
author: "mcmoyer"
date: "November 11, 2020"
output: html_document
---
  
## Step 1: select stimuli for experiment
  
Set your path here and load some packages that are necessary for visualization 
(ggplot), tidy data handling (tidyr and dplyr), and mixed effects modeling (lme4:
                                                                                                                                                               
```{r}  
setwd("/Users/momo/Dropbox/Stanford/whquestions-tgrep2/analysis/01_pilot/")
source("/Users/momo/Dropbox/Stanford/whquestions-tgrep2/analysis/helpers.R")
library(ggplot2)
library(tidyr)
library(dplyr)
library(lme4)
# theme_set(theme_bw())
```

Read the database into R and explore it.
```{r}
corp = read.table("/Users/momo/Dropbox/Stanford/whquestions-tgrep2/corpus/results/swbd.tab",sep="\t",header=T,quote="")
d = read.csv("/Users/momo/Dropbox/Stanford/whquestions-tgrep2/experiments/01_experiment/01_pilot/results/pilot_e01-merged.csv")

# Load in the .csv with the contexts removed
# d = read.csv("/Users/momo/Dropbox/Stanford/whquestions-tgrep2/corpus/swbd_nocntxt.csv",header=T)
View(corp)
# old
nrow(d) # 10667.....10278....10192 (added MACRO (@WH > /^WH/)...10199 (@WH >> /^WH)
head(d)
str(d)
summary(d)