---
title: "Analysis of factive verbs"
author: "mcmoyer"
date: "October 14, 2020"
output: html_document
---
  
## Step 1: select stimuli for experiment
  
Set your path here and load some packages that are necessary for visualization 
(ggplot), tidy data handling (tidyr and dplyr), and mixed effects modeling (lme4:
                                                                                                                                                               
```{r}  
setwd("/Users/morganmoyer/Dropbox/Stanford/whquestions-tgrep2/analysis/")
source("/Users/morganmoyer/Dropbox/Stanford/whquestions-tgrep2/analysis/helpers.R")
library(ggplot2)
library(tidyr)
library(dplyr)
library(lme4)
# theme_set(theme_bw())
```

Read the database into R and explore it.
```{r}
d = read.table("/Users/morganmoyer/Dropbox/Stanford/whquestions-tgrep2/corpus/results/swbd.tab",sep="\t",header=T,quote="")
nrow(d) # 10667
head(d)
str(d)
summary(d)
```

Take a random sample of 200.
```{r}
s = sample_n(d, 200)
View(s)

# save it to a csv file and provide an annotation guide for what 
# the different types of features should be
# overleaf. 

test = subset(d, d$QuestionType=="")
View(test)

```
(SBAR-TMP (WHADVP-1 (WRB when)) 
          (S  (NP-SBJ (PRP I)) 
              (VP (VBP 'm) (VP (VBG flying) 
                                (PP-LOC (IN in) (NP (DT an) (NN airplane)))
Wh-Adjunct

(TOP (S (NP-SBJ (PRP I)) 
        (VP (MD would) 
            (RB n't) 
            (VP (VP (VB want) 
                    (S (NP-SBJ (DT any) (NN air) (NN traffic) (NNS controllers)) 
                        (ADJP-PRD (JJ high)))) 
                    (CC or) 
                    (NP-ETC (NP (NN anything)) 
                            (PP (IN like) (NP (DT that)))) 
                    (SBAR-TMP (WHADVP-1 (WRB when)) (S (NP-SBJ (PRP I)) (VP (VBP 'm) (VP (VBG flying) (PP-LOC (IN in) (NP (DT an) (NN airplane))) (ADVP-TMP (-NONE- *T*-1)))))))) (. .) (-DFL- E_S)))



QuestionSubject

"where i work is predominantly male
(TOP (S (INTJ (UH Um)) 
    (, ,) 
    (SBAR-SBJ (WHADVP-1 (WRB where)) 
              (S (NP-SBJ (PRP I)) 
                  (VP (VBP work) (ADVP-LOC (-NONE- *T*-1))))) 
    (VP (VBZ is) (ADJP-PRD (RB predominantly) (NN male))) (. .) (-DFL- E_S)))
    
    
then whenever i have a meeting with a client *t*-4, i'll put a suit on. and then come home and get back into regular clothes again.

(TOP (S (ADVP (RB then)) 
    (SBAR-TMP (WHADVP-4 (WRB whenever)) 
              (S (NP-SBJ (PRP I)) (VP (VBP have) (NP (NP (DT a) (NN meeting)) (PP (IN with) (NP (DT a) 
              
whereas in this country where everyone respects the closed doors very much *t*-1, if you go out and then act like the lunatic you, you violate the, uh, the norms of social, of, um, public behavior.

(TOP (S (ADVP (IN Whereas)) 
        (PP-LOC (IN in) (NP (DT this) (NN country))) 
        (SBAR-LOC (WHADVP-1 (WRB where)) 
                  (S (NP-SBJ (NN everyone)) (VP (VBZ respects) (NP (DT the) (JJ closed) (NNS doors)) 


now the part about where you said 0 the apartment complex puts up signs that *t*-1 says no soliciting *t*-2,

(TOP (FRAG (INTJ (UH Now)) 
           (NP (NP (DT the) (NN part)) 
           (PP (IN about) (SBAR (WHADVP-2 (WRB where)) 
                                (S (NP-SBJ (PRP you)) 
                                    (VP (VBD said) (SBAR (-NONE- 0) (S (NP-SBJ (DT the) (NN apartment)
                                    
                                    
not what color you are *t*-1, how old you are *t*-2, what you're male or female.
(TOP (FRAG (RB not) 
          (SBAR (WHNP-1 (WDT what) (NN color)) 
                        (S (NP-SBJ (PRP you)) 
                          (VP (VBP are) 
                              (NP-PRD (-NONE- *T*-1))))) 
          (, ,) 
          (SBAR (WHADJP-2 (WRB how) (JJ old)) (S (NP-SBJ (PRP you)) (VP (VBP are) (ADJP-PRD (-NONE- *T*-2))))) 
          (, ,) 
          (SBAR (TYPO (WP what)) (S (NP-SBJ (PRP you)) (VP (VBP 're) (ADJP-PRD (JJ male) (CC or) (JJ female))))) (. .) (-DFL- E_S)))


3006:16
i'm not sure how long we're supposed *-1 to talk *t*-2.


	
i'm not sure why.

