---
title: "Analysis of factive verbs"
author: "mcmoyer"
date: "October 14, 2020"
output: html_document
---
  
## Step 1: select stimuli for experiment
  
Set your path here and load some packages that are necessary for visualization 
(ggplot), tidy data handling (tidyr and dplyr), and mixed effects modeling (lme4:
                                                                                                                                                               
```{r}  
setwd("/Users/morganmoyer/Dropbox/Stanford/whquestions-tgrep2/analysis/")
source("/Users/morganmoyer/Dropbox/Stanford/whquestions-tgrep2/analysis/helpers.R")
library(ggplot2)
library(tidyr)
library(dplyr)
library(lme4)
# theme_set(theme_bw())
```

Read the database into R and explore it.
```{r}
d = read.table("/Users/morganmoyer/Dropbox/Stanford/whquestions-tgrep2/corpus/results/swbd.tab",sep="\t",header=T,quote="")
nrow(d) # 10667.....10278
head(d)
str(d)
summary(d)
```

Take a random sample of 200.
```{r}
s = sample_n(d, 200)
View(s)

# save it to a csv file and provide an annotation guide for what 
# the different types of features should be
# overleaf. 

no_qt = subset(d, d$QuestionType=="")
nrow(no_qt) # 1016....819....20....18...0!
View(no_qt)

subj = subset(d, d$QuestionType=="subject")
View(subj)

```


	Level 0: 128 values of type 'fragment' were found.
	Level 1: 10002 values of type 'subject' were found.
	Level 2: 4471 values of type 'adjunct' were found.
	Level 3: 2130 values of type 'root' were found.
	Level 4: 3442 values of type 'embedded' were found.
	Level 5: 1908 values of type 'relative' were found.
	Level 6: 1828 values of type 'nominalized' were found.
	Level 7: 207 values of type 'exclamation' were found.

so that's why i'm planning and, and preparing for the, uh, education of my children, also try and set that money aside *t*-1.


and i can't see *-1 getting dressed up and wearing heels and stuff when you have *-2 to carry, you know, boxes of documents around *t*-3,
(TOP (S (CC and) 
        (NP-SBJ-1 (PRP I)) 
        (VP (MD ca) 
            (RB n't) 
            (VP (VB see) 
                (S (NP-SBJ (-NONE- *-1)) 
                   (VP (VP (VBG getting) 
                           (VP (VBN dressed) 
                               (PRT (RP up)))) 
                       (CC and) 
                       (VP (VBG wearing) (NP (NNS heels) 
                           (CC and) (NN stuff))) 
                       (SBAR-TMP (WHADVP-3 (WRB when)) 
                                (S (NP-SBJ-2 (PRP you)) (VP (VBP have) (S (NP-SBJ (-NONE- *-2)) (VP (TO to) (VP (VB carry) (PRN (, ,) (S (NP-SBJ (PRP you)) (VP (VBP know))) (, ,)) (NP (NP (NNS boxes)) (PP (IN of) (NP (NNS documents)))) (ADVP (RB around))))) (ADVP-TMP (-NONE- *T*-3))))))))) (, ,) (-DFL- E_S)))




		Level 0: 128 values of type 'fragment' were found.
		Level 1: 10278 values of type 'subject' were found.
		Level 2: 4471 values of type 'adjunct' were found.
		Level 3: 2130 values of type 'root' were found.
		Level 4: 3442 values of type 'embedded' were found.
		Level 5: 1908 values of type 'relative' were found.
		Level 6: 1828 values of type 'nominalized' were found.
		Level 7: 207 values of type 'exclamation' were found.


		Level 0: 128 values of type 'fragment' were found.
		Level 1: 10278 values of type 'subject' were found.
		Level 2: 4471 values of type 'adjunct' were found.
		Level 3: 976 values of type 'embadjunct' were found.
		Level 4: 2130 values of type 'root' were found.
		Level 5: 3442 values of type 'embedded' were found.
		Level 6: 1908 values of type 'relative' were found.
		Level 7: 1828 values of type 'nominalized' were found.
		Level 8: 207 values of type 'exclamation' were found.