---
title: "Analysis of factive verbs"
author: "mcmoyer"
date: "October 22, 2020"
output: html_document
---
  
## Step 1: select stimuli for experiment
  
Set your path here and load some packages that are necessary for visualization 
(ggplot), tidy data handling (tidyr and dplyr), and mixed effects modeling (lme4:
                                                                                                                                                               
```{r}  
setwd("/Users/momo/Dropbox/Stanford/whquestions-tgrep2/analysis/")
source("/Users/momo/Dropbox/Stanford/whquestions-tgrep2/analysis/helpers.R")
library(ggplot2)
library(tidyr)
library(dplyr)
library(lme4)
# theme_set(theme_bw())
```

Read the database into R and explore it.
```{r}
# d = read.table("/Users/momo/Dropbox/Stanford/whquestions-tgrep2/corpus/results/swbd.tab",sep="\t",header=T,quote="")

# Load in the .csv with the contexts removed
d = read.csv("/Users/momo/Dropbox/Stanford/whquestions-tgrep2/corpus/swbd_nocntxt.csv",header=T)
View(d)
# old
nrow(d) # 10667.....10278....10192 (added MACRO (@WH > /^WH/)...10199 (@WH >> /^WH)
head(d)
str(d)
summary(d)

View(d[1:26])
ncol(d)
names = colnames(d)

for(n in names) {
   d[n] <- as.factor(d$n)
    }
summary(d)

# d = as.factor(d[1:26])
str(d)
table(d$QuestionType)

nonya <- subset(s, s$QuestionType=="")
View(nonya)

nonya2 <- subset(d, d$QuestionType=="")
View(nonya2)
```

Take a random sample of 200.
```{r}
set.seed(123)
s <- sample_n(d, 200)
View(s)
nrow(s)
# write to CSV

write.csv(s, "whq_sample_200.csv",row.names = TRUE)

s_emb = subset(s, s$QuestionType=="embedded")
View(s_emb)

```
https://github.com/thegricean/corpus_implicatures/tree/master/or/experiments/4_implicature_exp/experiments/02_main/experiment_00/js

https://github.com/thegricean/corpus_implicatures/blob/master/some/experiments/main_experiments/speaker_knowledge/experiment_01/public/js/stimuli.js
https://raw.githubusercontent.com/leylakursat/some_without_context/master/experiment/corpora/corpus1.txt

https://thegricean.github.io/corpus_implicatures/or/experiments/4_implicature_exp/experiments/02_main/experiment_00/index.html


Reproduce the same set
```{r}
# the original DF i sent jd
sa <- read.csv("whq_sample_200_A.csv", header=TRUE)


dnew = semi_join(d, sa, by = c("Item_ID"))
nrow(dnew)


sa = sa[order(sa$Item_ID),]

ddnew = semi_join(sa, d, by=c("Item_ID"))
write.csv(ddnew, "whq_sample_200_neworig.csv",row.names = TRUE)

# try to check if they're the same IDs

ddnew_names = ddnew$Item_ID
sa_names = sa$Item_ID
length(sa_names)

all.equal(ddnew_names,sa_names)

View(ddnew)


snew = d %>%
  filter(Item_ID %in% sa$Item_ID)

write.csv(snew, "whq_sample_200_neworig.csv",row.names = TRUE)
# save it to a csv file and provide an annotation guide for what 
# the different types of features should be
# overleaf. 
# 
```

(TOP (S (INTJ (UH Uh)) 
        (, ,) 
        (NP-SBJ (NP (CD one)) 
                (PP (IN of) (NP (PRP$ its) (JJ great) (NNS slogans)))) 
        (VP (VBZ is) (SBAR-PRD (-NONE- 0) 
        (S (SBAR-ADV (IN if) (S (NP-SBJ (PRP you)) (VP (VBP 're) (RB not) (VP (VBG serving) (NP (DT the) (NN customer)))))) 
        (, ,) (NP-SBJ (PRP you)) (ADVP (RBR better)) 
        (VP (VB be) (VP (VBG serving) 
                        (NP (NP (NN someone)) 
                            (SBAR (WHNP-1 (WP who)) 
                                  (S (NP-SBJ (-NONE- *T*-1)) (VP (VBZ is) (NP-PRD (-NONE- *?*))))))))))) (. .) (-DFL- E_S)))


# some embedded cases aren't printing a matrix verb
```{r}
emb <- subset(d, d$QuestionType=="embedded")
nrow(emb)


enmv = emb %>%
  filter(MatrixPred1 %in% c(""))
nrow(enmv) # 3333.....0! fixed
View(enmv)

```

but it says 0 when the conversation is over *t*-1 * just say your good-byes and hang up.
(TOP (S (CC but) 
        (NP-SBJ (PRP it)) 
        (VP (VBZ says) 
            (SBAR (-NONE- 0) 
                  (S-IMP-SEZ (SBAR-TMP (WHADVP-1 (WRB when)) 
                                      (S (NP-SBJ (DT the) (NN conversation)) (VP (VBZ is) (ADVP-PRD (RP over)) (ADVP-TMP (-NONE- *T*-1))))) (NP-SBJ (-NONE- *)) (ADVP (RB just)) (VP (VP (VB say) (NP (PRP$ your) (NNS good-byes))) (CC and) (VP (VB hang) (PRT (RP up))))))) (. .) (-DFL- E_S)))



(TOP (S (CC And) (NP-SBJ (PRP I)) 
                  (VP (VBP think) 
                      (SBAR (IN that) 
                            (S (SBAR-TMP (WHADVP-1 (WRB when)) 
                                (S (NP-SBJ (PRP she)) (VP (VBD passed) (ADVP (RB away)) (ADVP-TMP (-NONE- *T*-1))))) (NP-SBJ (PRP it)) (VP (VBD was) (ADVP (RB probably)) (NP-PRD (NP (CD one)) (PP (IN of) (NP-UNF (DT the) (JJS greatest)))))))) (, ,) (-DFL- N_S)))


```{r}
no_qt = subset(d, d$QuestionType=="")
nrow(no_qt) # 1016....819....20....18...0!
View(no_qt)

mod = subset(d, d$ModalPresent=="yes")
nrow(mod) # 895

nmod = subset(d, d$ModalPresent=="no")
nrow(nmod) # 9235

table(d$ModalPresent)

nf2 <- subset(d, d$Finite=="no") # YES THESE ARE ALL GOOD
nrow(nf2) #190....186?
View(nf2)
# sanity check
nf <- subset(d, d$Finite!="yes") 
nrow(nf) #186
View(nf)

# Do these return all the same ?
all.equal(nf,nf2) # TRUE
````




````{r}
notmod = subset(d, d$ModalPresent!="no" & d$ModalPresent!="yes")
nrow(notmod)
View(notmod)
str(d)
notmodcomp = d %>%
  filter(!ModalPresent %in% c("yes","no")) %>%
  filter(WhPhraseType %in% c("complex"))

notmodcomp2 = subset(notmod, notmod$WhPhaseType=="complex")
nrow(notmodcomp2) # so there are non-complex wh that are failing
notmodnotcomp = subset(notmod, notmod$WhPhaseType!="complex")
nrow(notmodnotcomp)
View(notmodnotcomp)

```


```{r}
dd = grepl("can|could|may|might|must|shall|should", d$Sentence)
View(dd)

mods <- ""
for (r in notmod){
    if (grepl("can|could|may|might|must|shall|should", notmod$Sentence))
    mods + r
  }
```

Graphssss

```{r}
ftable(d$QuestionType,d$ModalPresent)

agr = d %>%
  group_by(QuestionType,ModalPresent,Finite) %>%
  mutate(count = count(Sentence), prop_modal= ) %>%
  
  ggplot(d, aes(x=as.factor(QuestionType),y=as.factor(Finite), fill = as.factor(ModalPresent))) +
  geom_bar()
  
View(agr)

```


