---
title: "Analysis of factive verbs"
author: "mcmoyer"
date: "October 14, 2020"
output: html_document
---
  
## Step 1: select stimuli for experiment
  
Set your path here and load some packages that are necessary for visualization 
(ggplot), tidy data handling (tidyr and dplyr), and mixed effects modeling (lme4:
                                                                                                                                                               
```{r}  
setwd("/Users/morganmoyer/Dropbox/Stanford/whquestions-tgrep2/analysis/")
source("/Users/morganmoyer/Dropbox/Stanford/whquestions-tgrep2/analysis/helpers.R")
library(ggplot2)
library(tidyr)
library(dplyr)
library(lme4)
# theme_set(theme_bw())
```

Read the database into R and explore it.
```{r}
d = read.table("/Users/morganmoyer/Dropbox/Stanford/whquestions-tgrep2/corpus/results/swbd.tab",sep="\t",header=T,quote="")
nrow(d) # 10667
head(d)
str(d)
summary(d)
```

Take a random sample of 200.
```{r}
s = sample_n(d, 200)
View(s)

# save it to a csv file and provide an annotation guide for what 
# the different types of features should be
# overleaf. 

test = subset(d, d$QuestionType=="")
nrow(test) # 1016....819
View(test)

```


and which *t*-1 isn't of, always the case in all cultures,
(TOP (SBAR (EDITED (RM (-DFL- \[)) 
                  (CC And) 
                  (IP (-DFL- \+)) 
                  (RS (-DFL- \]))) 
            (WHNP-1 (WDT which)) 
            (S (NP-SBJ (-NONE- *T*-1)) (VP (VBZ is) (RB n't) (EDITED (RM (-DFL- \[)) (PP-UNF (IN of)) (, ,) (IP (-DFL- \+)) (RS (-DFL- \]))) (ADVP-TMP (RB always)) (NP-PRD (DT the) (NN case)) (PP (IN in) (NP (DT all) (NNS cultures))))) (, ,) (-DFL- E_S)))


RELATIVE CLAUSE
now the part about where you said 0 the apartment complex puts up signs that *t*-1 says no soliciting *t*-2,
(TOP (FRAG (INTJ (UH Now)) 
      (NP (NP (DT the) (NN part)) 
          (PP (IN about) (SBAR (WHADVP-2 (WRB where)) (S (NP-SBJ (PRP you)) (VP (VBD said) (SBAR (-NONE- 0) (S (NP-SBJ (DT the) (NN apartment) (NN complex)) (VP (VBZ puts) (PRT (RB up)) (NP (NP (NNS signs)) (SBAR (WHNP-1 (WDT that)) (S (NP-SBJ (-NONE- *T*-1)) (VP (VBZ says) (NP-SEZ (DT no) (NN soliciting))))))))) (ADVP (-NONE- *T*-2))))))) (, ,) (-DFL- E_S)))


INFINITIVE CLAUSE

but, uh, they would be things on like how * to be successful *t*-1 and sort of * talking to yourself. you know ge-, getting your, yourself in gear * to, uh, sort of pull yourself up by your boot straps and do what you really want *-2 to do *t*-3. convincing you that you need *-4 to get on with it.

(TOP (S (CC but) (, ,) (INTJ (UH uh)) (, ,) (NP-SBJ (PRP they)) (VP (MD would) (VP (VB be) (NP-PRD (NP (NNS things)) (PP (IN on) (INTJ (UH like)) (UCP (SBAR (WHADVP-1 (WRB how)) (S (NP-SBJ (-NONE- *)) (VP (TO to) (VP (VB be) (ADJP-PRD (JJ successful)) (ADVP-MNR (-NONE- *T*-1)))))) (CC and) (S-NOM (ADVP (RB sort) (RB of)) (NP-SBJ (-NONE- *)) (VP (VP (VBG talking) (PP (IN to) (NP (PRP yourself)))) (PRN (. .) (S (NP-SBJ (PRP You)) (VP (VBP know)))) (EDITED (RM (-DFL- \[)) (VP-UNF (VBG ge-)) (, ,) (IP (-DFL- \+))) (VP (VBG getting) (RS (-DFL- \])) (EDITED (RM (-DFL- \[)) (NP-UNF (PRP$ your)) (, ,) (IP (-DFL- \+))) (S (NP-SBJ (PRP yourself)) (RS (-DFL- \])) (PP-PRD (IN in) (NP (NN gear)))) (S-PRP (NP-SBJ (-NONE- *)) (VP (TO to) (, ,) (INTJ (UH uh)) (, ,) (ADVP (RB sort) (RB of)) (VP (VP (VB pull) (NP (PRP yourself)) (PRT (RP up)) (PP (IN by) (NP (PRP$ your) (NN boot) (NNS straps)))) (CC and) (VP (VB do) (SBAR-NOM (WHNP-3 (WP what)) (S (NP-SBJ-2 (PRP you)) (ADVP (RB really)) (VP (VBP want) (S (NP-SBJ (-NONE- *-2)) (VP (TO to) (VP (VB do) (NP (-NONE- *T*-3))))))))))))) (. .) (VP (VBG Convincing) (NP (PRP you)) (SBAR (IN that) (S (NP-SBJ-4 (PRP you)) (VP (VBP need) (S (NP-SBJ (-NONE- *-4)) (VP (TO to) (VP (VB get) (PRT (RP on)) (PP (IN with) (NP (PRP it))))))))))))))))) (. .) (-DFL- E_S)))

